Mapping factors associated with adolescents' emotion dysregulation: A text-mining based systematic review

### 2020-12-23 manuscript.Rmd
Prepare for JOYA

abstract: |
  Adolesence is a developmentally sensititve period for emotion dysregulation.
  Although substantial empirical research has addressed relevant risk factors,
  the literature is fragmented across subdisciplines, and
  an integrating framework is lacking.
  This systematic review of 6305 papers used text mining to map correlates of adolescents’ (ages 10-25) emotion dysregulation. First, we established a baseline of relevant terms gleaned from theory and recent narrative reviews. Then, we conducted two text mining analyses to examine term/document frequency and co-occurrence in author-provided keywords and abstracts. Results reﬂected constructs commonly featured in theory and narrative reviews, but also identified underrepresented themes. This research constitutes a first step towards integrating the literature, and illustrates how text mining reviews may complement narrative reviews. <!--may inspire future empirical and theoretical work. SH: I would end with a more memorable take-home about how text-mining can be useful to researchers (e.g., when topics are of multi-disciplinary interest but each field has their own preferred methods and/or terminology)-->

@@

The present systematic review seeks to overcome these limitations by adopting a novel method:
the text mining based systematic review.
We set out to map the constructs associated with adolescent emotion regulation based on a systematic review of the empirical literature.
Traditional narrative literature reviews have been shown to be marred by reliance on small convenience samples of the literature, confirmation bias,
and an undue emphasis on positive results [@littellEvidencebasedBiasedQuality2008]. 
Text mining, by contrast, is uniquely suited to provide a comprehensive overview of the literature.
It can cover vastly greater corpora than a human reader,
and the process by which text mining gleans insights from the literature is more objective, transparant, and reproducible.
Where human readers might be inclined to structure their reading of the literature around established ideas,
the inherent "fairness" of text mining gives emerging themes in the literature a chance to come to the fore.
Text mining identifies important topics in a body of literature and reveals which constructs are often studied together.
This potentially reveals topics and connections missed by narrative reviewers,
thereby laying the groundwork for future empirical and theoretical work. <!-- CJ To fill out gaps, following up on promising constructs and unify heretofore disparate regions of the lit -->
<!-- SH: this implies that the main contribution of the paper is predominantly methodological is that the case? Is there some primary thesis/argument that will be advanced? It is really important to take a top-down approach to that messaging, beginning here in the first paragraph-->
<!-- Ergens anders: Similarly, although
there are several *relevant* theories, there is no specific theoretical
framework to guide research on adolescents' emotion regulation. Although theory
development is beyond the scope of this paper, we set out to generate a
proto-theoretical nomological network of the potential risk factors,
manifestations, and outcomes of emotion regulation in adolescence. We discuss
how this nomological network relates to existing relevant theory, and conclude
with recommendations for future theory-generating efforts.-->

@@

The results of our text mining analysis of the empirical literature are best understood against a backdrop of the existing theoretical landscape.
We therefore provide a summary theoretical review.
Other recent publications offer more detailed reviews of theories of emotional development [@bussTheoriesEmotionalDevelopment2019] and emotion regulation in adolescence [@riedigerEmotionRegulationAdolescence2014].
The correlates of emotion regulation difficulties discussed in the theoretical review below
are visually summarized in the left panel of Figure \@ref(fig:baseline)^[Based on an author-curated list of keywords, caterogized using the dictionary method introduced in Analysis 1.].

@@

Among the oldest relevant theories of adolescents' emotional development is Hall's notion of "storm and stress" [see
@arnettAdolescentStormStress1999]. It describes how `r keyw("hormonal")` changes diminish
`r keyw("self-control")` and increase `r keyw("reactivity")`, leading to difficulties in emotion
regulation, `r keyw("conflict with parents")`, and `r keyw("risky behavior")`.
In modern theories, this notion of diminished self-control and increased emotional reactivity has been retained - although it is now considered to be a normative change that facilitates emotional maturation
[@croneUnderstandingAdolescencePeriod2012], at the risk of emotional
disturbance [@arnettAdolescentStormStress1999; @leeAdolescentMentalHealth2014].

@@

This emphasis on social influences and `r keyw("neurocognitive development")` is reflected in many theories.
Some of these focus primarily on neurocognitive development.
For example, `r keyw("polyvagal theory")` closely links `r keyw("emotional experience")`
- and regulation - to autonomous nervous system functioning
[@porgesOrientingDefensiveWorld1995].
A more recent neurocognitive theory relevant to adolescents' emotion regulation development is Crone
and Dahl's model of social-affective engagement and `r keyw("goal flexibility")`
[@croneUnderstandingAdolescencePeriod2012]. Like other authors 
[e.g., @caseyBrakingAcceleratingAdolescent2011; @craccoEmotionRegulationChildhood2017],
Crone and Dahl argue that the developmental
asymmetry between `r keyw("motivational")` and inhibitory `r keyw("brain")` circuits gives rise to a
"maturity gap" in middle adolescence. 
What distinguishes Crone and Dahl from related writings
is the greater attention to adolescents' diverging destinies:
the question why some youngsters flourish while others languish.
They argue that adolescents' cognitive engagement is dynamically responsive to
social and motivational `r keyw("goal salience")`. This flexibility, on the one hand,
prepares adolescents to effectively engage cognitive systems in novel
challenging situations in a way that facilitates developing mature regulatory
abilities. On the other hand, it places them at risk to act impulsively in
pursuit of `r keyw("peer approval")`. In terms of explanans,
this theory focuses primarily on cognitive factors
and the role of peers, with less attention to factors such as parenting.
Although this theory focuses on adolescence specifically,
an important limitation is that it only tangentially relates to emotion regulation.

Other theories emphasize socialization to a greater extent.
One such theory is Morris' tripartite model, which focuses specifically on `r keyw("parents")`' role in emotion regulation development [-@morrisRoleFamilyContext2007].
It describes three pathways through which parents shape emotion regulation
development: Through observation and `r keyw("modeling")`, `r keyw("parenting practices")`, and the
emotional `r keyw("family climate")`, which in turn involves attachment and `r keyw("marital
relationship")` quality. Morris and colleagues emphasize the relevance of `r keyw("mothers")`, 
`r keyw("fathers")`, and siblings.
Others have adapted the tripartite model to describe
the role of peers in adolescents' emotion regulation development
[@reindlSocializationEmotionRegulation2016].
A more abstract take on socialization is found in @holodynskiDevelopmentEmotionsEmotion2006's
internalization model of emotional development. 
Unique aspects emphasized in this theory are the interplay between emotion and `r keyw("communication")`,
and the internalization of the `r keyw("cultural")` symbolic function of emotion.
These theories explain the process of socialization in great detail,
but one potential limitation is that they are not embedded in a larger unifying framework.
<!--Like Sroufe, Holodynski describes an age graded transition from
interpersonal to intrapersonal emotion regulation.
In doing so, Holodynski applies Vygotsky's theory of development to the domain of
emotion, and presents a detailed integrated model of emotional experience and
regulation.-->

Looking beyond the developmental literature,
theories of the phenomenon of emotion regulation offer additional insight into
intra-individual drivers of emotion regulation development.
Perhaps the most influential theory is Gross'
[-@grossHandbookEmotionRegulation2013] process model, which describes the
process of emotion regulation from eliciting cue to ultimate response.
According to Gross, individuals use `r keyw("strategies")` to modulate the different stages of this process,
consciously or otherwise. `r keyw("Culture")` plays a role too, as the effectiveness, desireability, and consequences of different strategies depend on the social context [see
@bariolaChildAdolescentEmotion2011]. Similar to Gross' theory, the social
information processing theory of emotion also describe the role of cognitive
processes and strategies in emotion experience and regulation
[@lemeriseIntegratedModelEmotion2000].

Finally, given our interest in risk factors that render adolescents susceptible
to emotional difficulties, we should mention two theories widely invoked to frame research on developmental influences: Bronfenbrenner's bioecological model, and Sameroff's
transactional model.
Bronfenbrenner's model
[@bronfenbrennerBioecologicalModelHuman2007] describes how the `r keyw("environment")`
shapes individual development. Each individual is imbued with certain
`r keyw("biological")` predispositions, and develops over time, in interaction with
contextual influences. These influences range from the microsystem, composed of
those people close to the individual, to the macrosystem, consisting of
indirect `r keyw("political")` and `r keyw("economic")` influences, to the exosystem, consisting of
cultural norms and values. Sameroff's model is somewhat compatible with the
bioecological model [@sameroffUnifiedTheoryDevelopment2010], but focuses more
on the interplay between nature and nurture. It conceptualizes development as a
product of reciprocal influences between the child and the environment.
Sameroff distinguishes between proximal influences, for instance, through
parents (the microsystem in Bronfenbrenner's model), and distal influences;
structural factors indirectly shaping development, like socio-economic status,
`r keyw("schools")`, and the `r keyw("community")` (macro- and exosystem). With increasing age, distal
influences gradually gain ground on proximal influences.
These theories are broad enough to contextualize any developmental study,
but lack specificity, which curtails their utility in generating hypotheses.
<!-- RK: What do you take from these broad perspectives for your RQ?-->
<!--SH I am not sure what contribution this paragraph ultimately makes - you should consider condensing it substantially to just note that these theories have something to say about emotional development but are not adolescent-specific-->
<!--Theories like this are particularly relevant to a fine-grained
understanding of the process of emotion regulation, but their developmental
relevance has unfortunately not yet been considered (REF Buss). -->
<!--Parents are widely considered to be the primary proximal influence driving
emotion regulation development.
Yet several limitations remain.
@coe-odessEmergentEmotionsAdolescence2019;
instead takes an inductive approach to map the correlates of adolescents'
emotion regulation based on all available literature.

@@

Despite the abundance of theory *relevant* to emotion regulation in adolescence,
the theoretical literature has several limitations.
First, few theories have explicitly addressed the life stage of adolescence. This life stage differs qualitatively from infancy, childhood, and adulthood [@bariolaChildAdolescentEmotion2011].
It is therefore questionable whether more general theories, or those focused on different age groups, can be generalized to adolescents.
<!--Relatedly, many relevant theories lack an explicit developmental component, which renders them and thus lack a well-substantiated
understanding of developmental processes[see
@bussTheoriesEmotionalDevelopment2019;
@croneUnderstandingAdolescencePeriod2012]. -->
Furthermore, few theories have comprehensively addressed important predictors of development in this life stage,
and none directly guide contemporary research in the field [see @bussTheoriesEmotionalDevelopment2019; @riedigerEmotionRegulationAdolescence2014].
Finally, available theories vary widely in scope:
Some are broad but somewhat non-specific, and others describe a specific phenomenon in detail,
but lack a broader perspective.
It would be beneficial to bridge these levels of analysis.
In sum, there is a need for more integrative theory formation,
in order to provide a unified framework that could guide future empirical work.<!--[see @riedigerEmotionRegulationAdolescence2014].
Inductive analysis of the empirical literature may constitute a first step to this end.-->
<!--Such a theory should focus on -->
The present study lays the groundwork for such theory development,
by providing a text-mining based inductive systematic review of the field.

@@

Whereas theory provides a top-down frame of reference for understanding a phenomenon,
literature reviews can provide a bottom-up, inductive understanding.
Given the noted absence of a single overarching theory, reviews might provide additional
insight into factors considered relevant in the etiology of adolescents'
emotion regulation competencies. 
Innovative text mining methods are promising in this respect, because they can comprehensively review the available literature.
Narrative reviews, however, constitute the status quo.
We will therefore examine how two excellent narrative reviews on emotion regulation in adolescence complement the aforementioned theoretical literature [@coe-odessEmergentEmotionsAdolescence2019; @bariolaChildAdolescentEmotion2011].
The right panel of Figure \@ref(fig:baseline) visually distinguishes constructs  uniquely covered by these narrative reviews,
relative to the issues also addressed in the theoretical literature (left panel).

@@

The seminal review by
@bariolaChildAdolescentEmotion2011 addresses individual psychological factors
such as temperament, and biological factors like neurocognitive development and
genetic predispositions. Furthermore, the authors address proximal social influences,
including parents, teachers, and peers, and specific mechanisms through which
these individuals exert their influence, including parenting and modeling.
Finally, they address distal factors, including the role of culture and the
media. Barriola and colleagues also 
<!--most notably, they call for a robust theoretical framework to guide future
research.--> call for future research to address parents' role beyond early
childhood.
They further argued that the role of fathers in emotion socialization warrants further scrutiny - a topic that is now receiving more attention [e.g., see @vanlissaRoleFathersMothers2019;
@vanlissaMothersFathersQuantitative2020].

A more recent review by @coe-odessEmergentEmotionsAdolescence2019 offers a nuanced
discussion of several issues that complement prior publications in this field.
For instance, the authors cover the implications of physiological changes in
detail, including neurocognitive development and pubertal maturation. As
adolescents become increasingly individuated, conflict with parents peaks. This
conflict, in turn, impacts emotion regulation, both in terms of day-to-day mood
variability and dispositional emotion dysregulation [see also
@vanlissaCostEmpathyParentadolescent2017].
Compared to children, adolescents also become increasingly oriented towards peers.
This includes increased
sensitivity to social status and norms, along with the associated increase in
peer pressure and risk taking. Pubertal development also initiates the
emergence of sexual and romantic behavior, and the intensification of both
biological sex differences and gender stereotyped behavior. With regard to the
process of emotion regulation, Coe-Odess and colleagues discuss the importance
of strategies, and point out that, in addition to negative emotionality,
positive emotionality also peaks in adolescence. Relatedly, the authors
describe how hormonal changes precipitate an increased stress response, which
might help explain adolescents' greater susceptibility to emotion
dysregulation. Finally, going beyond the implications of cognitive development
discussed in other publications, the authors discuss how an greater capacity
for abstract thought relates to identity formation - a key challenge in
adolescence [@meeusStudyAdolescentIdentity2011] - and to increased emotional
understanding, and by extension, empathy [see also
@vanlissaLongitudinalInterplayAffective2014].

As can be seen in Figure \@ref(fig:baseline), 
there are notable parallels between the relevant factors highlighted by these
narrative reviews, and the aforementioned theoretical literature.
Nevertheless,
these literature reviews also touch upon issues that have received little
attention in theoretical work.
These include specific individual differences at the biological and psychological level, including genetic predisposition, hormones, pubertal onset, gender, sexuality, temperament, identity, empathy, and stress.
Further introduced are proximal influences, including the role of media, norms, and social status.
This illustrates that reviews of the empirical literature can contribute additional insight into key factors in adolescents' emotion regulation development.
However, an important remaining limitation is that all reviews in this field have been unstructured narrative reviews, which are known to be limited in scope and biased [@littellEvidencebasedBiasedQuality2008].
We seek to complement preceding work by using text mining to conduct a more comprehensive empirical
literature review, and map the factors associated with adolescent emotion
regulation.

@@

The present paper aims to map the constructs
related to adolescent emotion dysregulation, based on a systematic review of
the literature. <!-- CJ Consider removing the following if the purpose is sufficiently clarified in the introduction -->
First, we conducted a systematic search to
elicit a corpus of relevant literature. Second, we used text mining techniques
to extract relevant constructs from the corpus. Third, we used a dictionary to
pare down the extracted constructs to meaningful superordinate categories.
Fourth, we mapped interrelations between these constructs. Fifth, we classified
contstructs as potential predictors or outcomes.
<!--, and we categorize predictors
by level of analysis-->
<!-- (CJ: Sameroff, which level of biopsychosocial)-->.
<!-- t, using text mining to map potential predictors of adolescent emotion
dysregulation.
identify relevant constructs of adolescents’ emotion regulation development,
and moderators of parents’ role therein. The resulting insights are
consolidated into theory.
The present study intends to map the extant literature
First, I will systematically review predictors currently considered relevant in
the adolescent emotion regulation literature.  -->

@@

All searches were conducted on Web of Science,
the most comprehensive database for which we had permissions for exporting keywords and abstracts.
The search strategy was based on
procedures described by Staaks [@staaksSystematicReviewSearch]. First, we
manually constructed a reference set of 15 articles. Then we constructed a
search string to retrieve these articles from Web of Science. The search was
overly inclusive, returning 29 records.
As these were all highly relevant, we
updated the reference set to include all 29 results.
Next, we tested our search string, which consisted of synonyms of emotion regulation and adolescence: <!--
### Reference set Our reference set is documented in `reference_set.bib`. -->
```
TS=("emotio* regulation" OR "anger regulation" OR "sadness regulation" OR
"emotion* competence" OR "emotion* adjustment" OR "emotio* dysregulation" OR
"anger dysregulation" OR "sadness dysregulation" OR "emotio* problem*" OR
"emotion* maladjustment") AND TS=(adolescent* OR teen* OR pubert* OR youth)
```
This string returned 6653 results, and matched 25 of the 29 records in the
reference set. To match all 29 reference set items,
three additional terms would have to be added to the search string.
Adding the terms `"emotio* socialization" OR "emotio* processes"`, as synonyms for emotion regulation,
would result in 191 more hits, most of which did not meet the inclusion criteria used for screening, as explained below.
Adding the term `"development*"`, as synonym of adolescence, added 3628 new hits,
many of which were not focused on adolescence.
We thus deemed these terms to be overly inclusive, and
proceeded with the original search string above.
```{r readrecs}
filenam <- "recs_6653.RData"
if(!file.exists(filenam)){
  library(bibliometrix)
  f <- list.files("./recs/18-3-2020/", full.names = TRUE)
  f <- readFiles(f)
  recs <- convert2df(f)
  saveRDS(recs, filenam)
} else {
  recs <- readRDS(filenam)
}
```

## Deduplication

@@

```
Duplicates were identified based on exact DOI matches (`r dups[["dup_doi"]]` 
duplicates), and title similarity (`r dups[["dup_title"]]` duplicates). 
Manual screening in Rayyan resulted in the removal of an additional `r rayyan_dups` duplicates.

@@

if(!file.exists("recs_final.csv")){
  recs_final <- unique_recs[screen$key[!screen$drop_these], ]
  write.csv(recs_final, "recs_final.csv", row.names = FALSE)
} else {
  recs_final <- read.csv("recs_final.csv")
}
```
Papers were screened based on two main criteria:
First, papers had to address emotion regulation or a synonymous construct.
Second, the target population must overlap with the life stage of adolescence,
defined as the age range from 10-24.
Thus, for example, an article reviewing the role of hormonal changes in emotional adjustment throughout the entire life course, including adolescence, would be deemed relevant.
Preliminary screening was conducted in Rayyan QRCI [@Ouzzani2016].
Papers were sorted using Rayyan's ranking algorithm.
To train the algorithm on exclusion criteria, screening focused on abstracts most likely to be excluded.
After coding `r sum(screen$rayyan == "True")+sum(screen$rayyan == "False")` papers, screening continued in ASReview - a free, open source alternative to Rayyan QRCI [@van_de_schoot_rens_2020_3828293].
This program uses active learning to build a customizable machine learning model for article inclusion.
We used a naive Bayes model, and focused on exclusion of irrelevant papers.
In ASReview, an additional `r sum(table(screen$included, screen$rayyan)[, 1])` papers were screened.
Screening again focused on articles most likely to be excluded, and continued until, among the most recently screened 100 papers, only 6 were excluded.
The screening procedure is detailed in Figure \@ref(fig:prismachart).
In total, `r nrow(recs_final)` papers were retained for analysis.

```{r prismachart, results='asis', fig.cap="Record screening flowchart"}
library(tidySEM)

@@

```{r}
source("word_functions.R")
source("circle2.R")
```

>>>>

abstract: |
  Adolesence is a developmentally sensititve period for emotion dysregulation.
  Although substantial empirical research has addressed relevant risk factors,
  the literature is fragmented across subdisciplines, and
  an integrating framework is lacking.
  This systematic review of 6305 papers used text mining to map correlates of adolescents’ (ages 
  10-25) emotion dysregulation. First, we established a baseline of relevant terms gleaned from 
  theory and recent narrative reviews. Then, we conducted two text mining analyses to examine 
  term/document frequency and co-occurrence in author-provided keywords and abstracts. Results 
  reﬂected constructs commonly featured in theory and narrative reviews, but also identified 
  underrepresented themes. This research constitutes a first step towards integrating the 
  literature, and illustrates how text mining reviews may complement narrative reviews.

@@

The present systematic review addressed these limitations by adopting a novel method:
the text mining based systematic review.
We set out to map the constructs associated with adolescent emotion regulation based on a systematic review of the empirical literature.
Traditional narrative literature reviews have been shown to be marred by reliance on small convenience samples of the literature, confirmation bias,
and an undue emphasis on positive results [@littellEvidencebasedBiasedQuality2008]. 
Text mining, by contrast, is uniquely suited to provide a comprehensive overview of the literature.
It can cover vastly greater corpora than a human reader,
and the process by which text mining gleans insights from the literature is more objective, transparant, and reproducible.
Where human readers might be inclined to structure their reading of the literature around established ideas,
the inherent "fairness" of text mining gives emerging themes in the literature a chance to come to the fore.
Text mining identifies important topics in a body of literature and reveals which constructs are often studied together.
This potentially reveals topics and connections missed by narrative reviewers,
thereby laying the groundwork for future empirical and theoretical work. <!-- CJ To fill out gaps, following up on promising constructs and unify heretofore disparate regions of the lit -->
<!-- SH: this implies that the main contribution of the paper is predominantly methodological is that the case? Is there some primary thesis/argument that will be advanced? It is really important to take a top-down approach to that messaging, beginning here in the first paragraph-->
<!-- Ergens anders: Similarly, although
there are several *relevant* theories, there is no specific theoretical
framework to guide research on adolescents' emotion regulation. Although theory
development is beyond the scope of this paper, we set out to generate a
proto-theoretical nomological network of the potential risk factors,
manifestations, and outcomes of emotion regulation in adolescence. We discuss
how this nomological network relates to existing relevant theory, and conclude
with recommendations for future theory-generating efforts.-->

@@

Our text mining analysis of the empirical literature is best understood against a backdrop of the existing theoretical landscape.
We therefore provide a summary theoretical review.
Other recent publications offer more detailed reviews of theories of emotional development [@bussTheoriesEmotionalDevelopment2019] and emotion regulation in adolescence [@riedigerEmotionRegulationAdolescence2014].
The correlates of emotion regulation difficulties discussed in our theoretical review
are summarized in Figure \@ref(fig:baseline)^[Based on an author-curated list of keywords, caterogized using the dictionary method introduced in Analysis 1.].

@@

Among the oldest relevant theories of adolescents' emotional development is Hall's notion of "storm and stress" [see
@arnettAdolescentStormStress1999]. It describes how `r keyw("hormonal")` changes diminish
`r keyw("self-control")` and increase `r keyw("reactivity")`, leading to emotion
dysregulation, `r keyw("conflict with parents")`, and `r keyw("risky behavior")`.
This notion of diminished self-control and increased emotional reactivity persists in modern theory, but is now considered a normative change that facilitates emotional maturation
[@croneUnderstandingAdolescencePeriod2012], at the risk of emotional
disturbance [@arnettAdolescentStormStress1999; @leeAdolescentMentalHealth2014].

@@

This emphasis on social influences and `r keyw("neurocognitive development")` is reflected in many theories.
Some of these focus primarily on neurocognitive development.
For example, `r keyw("polyvagal theory")` closely links `r keyw("emotional experience")`
- and regulation - to autonomous nervous system functioning
[@porgesOrientingDefensiveWorld1995].
More recently, in their model of social-affective engagement and `r keyw("goal flexibility")`
<!--. Like other authors 
[e.g., @caseyBrakingAcceleratingAdolescent2011; @craccoEmotionRegulationChildhood2017],
Crone and Dahl--> Crone and Dahl [-@croneUnderstandingAdolescencePeriod2012] posited that the developmental 
asymmetry between `r keyw("motivational")` and inhibitory `r keyw("brain")` circuits gives rise to a
"maturity gap" in middle adolescence. 
What distinguishes Crone and Dahl from related writings [e.g., @craccoEmotionRegulationChildhood2017]
is the emphasis on adolescents' diverging destinies;
why some youngsters flourish while others languish.
They argue that adolescents' cognitive engagement is dynamically responsive to
social and motivational `r keyw("goal salience")`.
This flexibility <!--, on the one hand,-->
prepares adolescents to <!--effectively engage cognitive systems in novel
challenging situations in a way that facilitates--> develop mature regulatory
abilities, but also places them at risk of impulsivity in
pursuit of `r keyw("peer approval")`. In terms of explanans,
this theory focuses primarily on cognitive factors
and the role of peers, with less attention to factors such as parenting.
This theory is relevant because it focuses on adolescence specifically,
but only tangentially addresses emotion regulation.

Other theories emphasize socialization to a greater extent,
such as Morris' tripartite model, which focuses on `r keyw("parents")`'
role in emotion regulation development [-@morrisRoleFamilyContext2007].
It describes three pathways through which parents shape emotion regulation
development: `r keyw("modeling")`, `r keyw("parenting practices")`, and the
emotional `r keyw("family climate")`,
which subsumes attachment and `r keyw("marital relationship")` quality.
Morris emphasizes the relevance of `r keyw("mothers")`, 
`r keyw("fathers")`, and siblings.
Others have adapted the tripartite model to describe peers' role in emotion regulation socialization
[@reindlSocializationEmotionRegulation2016].
A more abstract take on socialization is found in @holodynskiDevelopmentEmotionsEmotion2006's
internalization model of emotional development. 
Hallmarks of this theory are the interplay between emotion and `r keyw("communication")`,
and the internalization of the `r keyw("cultural")` symbolic function of emotion.
Several theories thus explain emotion regulation socialization in detail,
but a potential limitation is that they are not embedded in a larger unifying framework.
<!--Like Sroufe, Holodynski describes an age graded transition from
interpersonal to intrapersonal emotion regulation.
In doing so, Holodynski applies Vygotsky's theory of development to the domain of
emotion, and presents a detailed integrated model of emotional experience and
regulation.-->

Theories of the phenomenon of emotion regulation offer insight into
intra-individual drivers of emotion regulation development.
Gross' [-@grossHandbookEmotionRegulation2013] influential process model describes the
phenomenon of emotion regulation, from eliciting cue to ultimate response.
According to Gross, individuals use `r keyw("strategies")` to modulate the different stages of this process,
consciously or otherwise. The effectiveness, desireability, and consequences of some strategies vary across `r keyw("culture")`s [see
@bariolaChildAdolescentEmotion2011].
Similar to Gross' theory, the "social
information processing" theory also describes the role of cognitive
processes and strategies in emotion regulation
[@lemeriseIntegratedModelEmotion2000].
One limitation of these theories in the present context is the lack of a developmental component.

Finally, given our interest in risk factors that render adolescents susceptible
to emotional difficulties, we should mention two theories widely invoked to frame research on developmental influences: Bronfenbrenner's bioecological model, and Sameroff's
transactional model.
Bronfenbrenner [-@bronfenbrennerBioecologicalModelHuman2007] describes how the `r keyw("environment")`
shapes individual development.
Each individual is imbued with `r keyw("biological")` predispositions,
and develops in interaction with contextual influences.
These influences range from the microsystem,
composed of people close to the individual,
to the macrosystem, consisting of `r keyw("political")` and `r keyw("economic")` influences,
to the exosystem, consisting of `r keyw("cultural")` norms and `r keyw("values")`.
Sameroff's model [-@sameroffUnifiedTheoryDevelopment2010] is compatible with Bronfenbrenner's work,
but focuses more on the interplay between nature and nurture.
It conceptualizes development as a product of reciprocal influences between child and environment.
Sameroff distinguishes proximal influences such as parents (the microsystem in Bronfenbrenner's model)
from distal influences;
structural factors indirectly shaping development, like `r keyw("socio-economic status")`,
`r keyw("schools")`, and the `r keyw("community")` (macro- and exosystem).
With increasing age, distal influences gain ground on proximal influences.
These theories are broad enough to contextualize any developmental study,
but lack specificity, which curtails their utility in generating hypotheses.
<!-- RK: What do you take from these broad perspectives for your RQ?-->
<!--SH I am not sure what contribution this paragraph ultimately makes - you should consider condensing it substantially to just note that these theories have something to say about emotional development but are not adolescent-specific-->
<!--Theories like this are particularly relevant to a fine-grained
understanding of the process of emotion regulation, but their developmental
relevance has unfortunately not yet been considered (REF Buss). -->
<!--Parents are widely considered to be the primary proximal influence driving
emotion regulation development.
Yet several limitations remain.
@coe-odessEmergentEmotionsAdolescence2019;
instead takes an inductive approach to map the correlates of adolescents'
emotion regulation based on all available literature.

@@

Despite the abundance of theory *relevant* to emotion regulation in adolescence,
the literature has several limitations.
First, few theories have explicitly addressed adolescence.
This life stage differs qualitatively from both childhood and adulthood [@bariolaChildAdolescentEmotion2011].
It is therefore questionable whether theories focused on different age groups can be generalized to adolescents.
<!--Relatedly, many relevant theories lack an explicit developmental component, which renders them and thus lack a well-substantiated
understanding of developmental processes[see
@bussTheoriesEmotionalDevelopment2019;
@croneUnderstandingAdolescencePeriod2012]. -->
Furthermore, few theories have comprehensively addressed important predictors of development in this life stage,
and none directly guide contemporary research in the field [see @bussTheoriesEmotionalDevelopment2019; @riedigerEmotionRegulationAdolescence2014].
Finally, existing theories vary widely in scope:
Some are broad and non-specific; others describe a specific phenomenon in detail,
but lack a broader perspective.
It would be beneficial to bridge these levels of analysis.
In sum, there is a need for more integrative theory formation,
in order to provide a unified framework that could guide future empirical work.<!--[see @riedigerEmotionRegulationAdolescence2014].
Inductive analysis of the empirical literature may constitute a first step to this end.-->
<!--Such a theory should focus on -->
The present study lays the groundwork for such theory development,
by providing a text-mining based inductive systematic review of the field.

@@

Whereas theory provides a top-down frame of reference,
literature reviews can provide a bottom-up, inductive understanding of a phenomenon.
Given the noted absence of a single overarching theory, reviews might provide additional
insight into factors considered relevant in the etiology of adolescents'
emotion regulation competencies. 
Innovative text mining methods are promising in this respect, because they can comprehensively review the available literature.
Narrative reviews, however, constitute the status quo.
We will therefore examine how two excellent narrative reviews on emotion regulation in adolescence complement the aforementioned theoretical literature [@coe-odessEmergentEmotionsAdolescence2019; @bariolaChildAdolescentEmotion2011].
Figure \@ref(fig:baseline) visualizes constructs uniquely covered by these narrative reviews,
relative to the theoretical literature.

@@

A seminal review by
@bariolaChildAdolescentEmotion2011 addressed intra-individual factors
such as temperament, and biological factors like neurocognitive development and
genes.
Proximal social influences covered include socialization and modeling by parents, teachers, and peers.
Finally, distal factors include the role of culture and the
media.
Barriola and colleagues made several suggestions for future research,
calling for a robust theoretical framework to guide future
research, for research on parents' role beyond early childhood,
and for additional work on the role of fathers in emotion socialization.
The latter two topics are now receiving more attention [e.g., see @vanlissaRoleFathersMothers2019;
@vanlissaMothersFathersQuantitative2020].

A recent review by @coe-odessEmergentEmotionsAdolescence2019 offers a nuanced
discussion of several issues that complement prior publications.
This includes the implications of physiological changes,
including neurocognitive development and pubertal maturation.
Conflict with parents is addressed too, which peaks when adolescents become increasingly individuated.
Such conflict impacts both day-to-day mood swings and dispositional emotion dysregulation [see also
@vanlissaCostEmpathyParentadolescent2017].
Adolescents also become increasingly oriented towards peers.
This increases sensitivity to social status and norms,
along with concomitant increases in peer pressure and risk taking.
Pubertal development further precipitates sexual and romantic behavior,
and the intensification of both biological sex differences and gender stereotyped behavior.
<!--With regard to the process of emotion regulation,
Coe-Odess and colleagues discuss the importance
of strategies, and point out that, in addition to negative emotionality,
positive emotionality also peaks in adolescence. -->
Relatedly, the authors describe how hormonal changes intensify the stress response,
which helps explain adolescents' greater susceptibility to emotion dysregulation.
Finally, <!--going beyond the implications of cognitive development
discussed in other publications,--> the authors discuss how cognitive development and increased capacity
for abstract thought relate to identity formation - a key challenge in
adolescence [@meeusStudyAdolescentIdentity2011] - and to increased emotional
understanding, and by extension, empathy [see also
@vanlissaLongitudinalInterplayAffective2014].

As can be seen in Figure \@ref(fig:baseline), 
there are notable parallels between correlates of emotion regulation identified in these
narrative reviews, and in the preceding theoretical literature.
Nevertheless,
these literature reviews also touch upon issues that have received little
attention in theoretical work.
<!--These include specific individual differences at the biological and psychological level, including genetic predisposition, hormones, pubertal onset, gender, sexuality, temperament, identity, empathy, and stress.
Further introduced are proximal influences, including the role of media, norms, and social status.-->
This illustrates that reviews of the empirical literature can contribute additional insight into key factors in adolescents' emotion regulation development.
An important limitation is that all reviews in this field have been unstructured narrative reviews, which are known to be limited in scope and biased [@littellEvidencebasedBiasedQuality2008].
We seek to complement preceding work by using text mining to conduct a more comprehensive empirical
literature review, and map the factors associated with adolescent emotion
regulation.

@@

The present paper aims to map the constructs
related to adolescent emotion dysregulation, based on a systematic review of
the literature. <!-- CJ Consider removing the following if the purpose is sufficiently clarified in the introduction -->
First, we conducted a systematic search to
elicit a corpus of relevant literature. Second, we used text mining techniques
to extract relevant constructs from the corpus. Third, we used a dictionary to
pare down the extracted constructs to meaningful superordinate categories.
Fourth, we mapped interrelations between these constructs. Fifth, we classified
contstructs as potential predictors or outcomes.
We used the Workflow for Open Reproducible Code in Science (WORCS)
to ensure transparency and  reproducibility. All code and data are available online at [masked].

@@

We searched Web of Science,
the most comprehensive database for which we had permissions to export keywords and abstracts.
The search strategy was based on
procedures described by Staaks [@staaksSystematicReviewSearch]. First, we
constructed a reference set of 29 articles.
Then we constructed a search string to retrieve this set.
The search string consisted of synonyms of emotion regulation and adolescence.
It returned 6653 results, including 25 records in the reference set.
To match all 29 reference set items required adding the terms `"emotio* socialization" OR "emotio* processes"` as synonyms for emotion regulation.
Doing so resulted in 191 more hits, most of which did not meet the inclusion criteria explained below.
We thus deemed these terms to be overly inclusive, and
proceeded with the original search string above.
```{r readrecs}
filenam <- "recs_6653.RData"
if(!file.exists(filenam)){
  library(bibliometrix)
  f <- list.files("./recs/18-3-2020/", full.names = TRUE)
  f <- readFiles(f)
  recs <- convert2df(f)
  saveRDS(recs, filenam)
} else {
  recs <- readRDS(filenam)
}
```

@@

@@

if(!file.exists("recs_final.csv")){
  recs_final <- unique_recs[screen$key[!screen$drop_these], ]
  write.csv(recs_final, "recs_final.csv", row.names = FALSE)
} else {
  recs_final <- read.csv("recs_final.csv")
}
```
The screening and deduplication procedure is detailed in Figure \@ref(fig:prismachart).
Duplicates were identified using DOI and title similarity.
Papers were screened based on two main criteria:
They had to address emotion regulation or a synonymous construct, and the target population must overlap with the age range of adolescence (10-24).
Preliminary screening was conducted in Rayyan QRCI [@Ouzzani2016].
After coding `r sum(screen$rayyan == "True")+sum(screen$rayyan == "False")` papers, screening continued in ASReview [@van_de_schoot_rens_2020_3828293].
This program uses machine learning to screen articles.
We trained the machine learning algorithm by manually screening an additional `r sum(table(screen$included, screen$rayyan)[, 1])` papers, until - among the most recently screened 100 papers - only 6 were excluded.
In total, `r nrow(recs_final)` papers were deemed suitable for analysis.

```{r prismachart, results='asis', fig.cap="Record screening flowchart"}
if(!isTRUE(tools::md5sum("prismachart.png") == "08351426aee2005edd1332a32b958ea0" )){
  library(tidySEM)

@@

```{r}
library(stringr)
library(udpipe)
library(igraph)
library(wordcloud)
library(Matrix)
library(yaml)
library(Rmpfr)
library(topicmodels)
library(udpipe)
library(slam)
library(tidytext)
library(ggplot2)
library(textrank)
source("word_functions.R")
source("circle2.R")
